Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-13 paper.tex
Abstract proposal

We associate to each goal in Aesop's search tree a partial match state that reflects the goal's context.
Let $\States$ be the set of partial match states, $\Hyps$ the set of hypotheses, $\Rules$ the set of rules, $\CMatches$ the set of complete matches and $\powerset(X)$ the powerset of $X$.
The partial match state's interface then consists of two functions:
\begin{align*}
  \addHyp &: \States → \Hyps → \States × \powerset(\Rules × \CMatches) \\
  \delHyp &: \States → \Hyps → \States
\end{align*}
The $\addHyp$ function adds a hypothesis to the partial match state.
Hence, if $s$ is the partial match state corresponding to context $Γ$ and $\addHyp(s, h : T) = (s', M)$, then $s'$ is the partial match state corresponding to $Γ,\, h : T$.
Similarly, if $s$ is the partial match state corresponding to $Γ, h : T$, then $\delHyp(s, h : T)$ is the partial match state corresponding to $Γ$.
The second output of $\addHyp$, $M$, is a set of pairs $(r, m)$ where $r$ is a rule and $m$ is a complete match for $r$.
These are the matches that were completed by adding $h : T$.

>>>>

We associate to each goal in Aesop's search tree a partial match state that reflects the goal's context.
Let $\States$ be the set of forward match states, $\Hyps$ the set of hypotheses, $\Rules$ the set of rules and $\CMatches$ the set of complete matches.
The forward match state's interface then consists of two functions:
\begin{align*}
  \addHyp &: \States → \Hyps → \States × \powerset(\Rules × \CMatches) \\
  \delHyp &: \States → \Hyps → \States
\end{align*}
The $\addHyp$ function adds a hypothesis to the partial match state.
Hence, if $s$ is the partial match state corresponding to context $Γ$ and $\addHyp(s, h : T) = (s', M)$, then $s'$ is the partial match state corresponding to $Γ,\, h : T$.
Similarly, if $s$ is the partial match state corresponding to $Γ, h : T$, then $\delHyp(s, h : T)$ is the partial match state corresponding to $Γ$.
The second output of $\addHyp$, $M$, is a set of pairs $(r, m)$ where $r$ is a rule and $m$ is a complete match for $r$.
These are the matches that were completed by adding $h : T$.
